---
title: "workshop_example_v3"
author: "Dorian"
date: "2024-11-30"
output: html_document
---
```{r data generation, echo = FALSE, results = "hide"}
library(exams)

# Random selection for element
element <- sample(c("H", "O"), 1)

# Atomnummern
atomic_numbers <- list(H = 1, O = 8)

# Fragetext abhängig vom gewählten Element
element_text <- switch(
  element,
  H = "hydrogen",
  O = "oxygen"
)

# Define the molar masses of hydrogen (H) and oxygen (O)
m_h <- 1.008 # molar mass of hydrogen in g/mol
m_o <- 16.00 # molar mass of oxygen in g/mol

# Define possible compounds of hydrogen and oxygen
compounds <- list(
  H2O = list(name = "water ($H_2O$)", H = 2, O = 1),
  H2O2 = list(name = "hydrogen peroxide ($H_2O_2$)", H = 2, O = 2),
  OH = list(name = "hydroxide ion ($OH^-$)", H = 1, O = 1)
)

# Randomly choose one compound for the molar mass question
chosen_compound <- sample(names(compounds), 1)
compound_data <- compounds[[chosen_compound]]

# Calculate the molar mass of the chosen compound
m_compound <- compound_data$H * m_h + compound_data$O * m_o

# Dynamically set the question text for molar mass
compound_text <- compound_data$name
```

```{r answers/solutions, echo = FALSE, results = "hide"}
# Create lists for necessary information
answers <- list()
solutions <- list()
types <- list()
explanations <- list()
tolerances <- list()

# Define Question 1: atomic number of chosen element
answers[[1]] <- ""  # No predefined answer for numeric
solutions[[1]] <- atomic_numbers[[element]]
types[[1]] <- "num" #numeric
explanations[[1]] <- paste0("The atomic number of ", element_text,
                            " is ", atomic_numbers[[element]], 
                            " because it has that many protons in its nucleus.")
tolerances[[1]] <- 0  # No tolerance

# Define Question 2: molar mass of chosen compound
answers[[2]] <- "" # no predefined answer for numeric
solutions[[2]] <- m_compound
types[[2]] <- "num" 
explanations[[2]] <- paste0("The molar mass of ", compound_text," is calculated by adding the molar masses of ", compound_data$H, " hydrogen atoms and  ", compound_data$O, " oxygen atom.")
tolerances[[2]] <- 0.5 # Allow for small rounding errors
```

Question
========

*Questions 1*

What is the atomic number of `r element_text` in the periodic table?
##ANSWER1##

*Question 2*

Calculate the molar mass of `r compound_text`. Use the following molar masses:

- Hydrogen ($H$): `r m_h` $g/mol$

- Oxygen ($O$): `r m_o` $g/mol$

Provide your answer in grams per mole ($g/mol$).
##ANSWER2##

```{r questionlist, echo = FALSE, results = "asis", results = "hide"}
answerlist(unlist(answers), markup = "markdown")
```

Solution
========
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(unlist(explanations), markup = "markdown")
```

$M_{H_{2}O} = 2 \cdot M_H + M_O = 2 \cdot `r m_h` + `r m_o` = `r m_h2o`$ (g/mol)


Meta-information
================
exname: example_num
extitle: molmass of water 
extype: cloze
exsolution: `r paste(solutions, collapse = "|")`
exclozetype: `r paste(types, collapse = "|")`
extol: `r paste(tolerances, collapse = "|")`
exshuffle: TRUE
exversion: v1