---
title: "workshop_example_v2"
author: "Dorian"
date: "2024-11-30"
output: html_document
---
```{r data generation, echo = FALSE, results = "hide"}
library(exams)

# Random selection for element
set.seed(sample(1e3, size = 1)) 
element <- sample(c("H", "O"), 1)

# Define atomic numbers
atomic_numbers <- list(H = 1, O = 8)

# text module according to element
element_text <- switch(
  element,
  H = "hydrogen",
  O = "oxygen"
)

# Define the molar masses of hydrogen (H) and oxygen (O)
m_h <- 1.008 # molar mass of hydrogen in g/mol
m_o <- 16.00 # molar mass of oxygen in g/mol

# Calculate the molar mass of the water molecule (H2O)
m_h2o <- 2 * m_h + m_o
```

```{r answers/solutions, echo = FALSE, results = "hide"}
# Create lists for necessary information
answers <- list()
solutions <- list()
types <- list()
explanations <- list()
tolerances <- list()

# Define Question 1: atomic number of hydrogen or oxygen
answers[[1]] <- ""  # No predefined answer for numeric
solutions[[1]] <- atomic_numbers[[element]]
types[[1]] <- "num" #numeric
explanations[[1]] <- paste0("The atomic number of ", element_text,
                            " is ", atomic_numbers[[element]], 
                            " because it has that many protons in its nucleus.")
tolerances[[1]] <- 0  # No tolerance

# Define Question 2: molar mass of water
answers[[2]] <- "" # no predefined answer for numeric
solutions[[2]] <- m_h2o
types[[2]] <- "num" 
explanations[[2]] <- "The molar mass of H2O is calculated by adding the molar masses of two hydrogen atoms and one oxygen atom."
tolerances[[2]] <- 0.5 # Allow for small rounding errors
```

Question
========

*Questions 1*

What is the atomic number of `r element_text` in the periodic table?
##ANSWER1##

*Question 2*

Calculate the molar mass of water ($H_2O$). Use the following molar masses:

- Hydrogen ($H$): `r m_h` $g/mol$

- Oxygen ($O$): `r m_o` $g/mol$

Provide your answer in grams per mole ($g/mol$).
##ANSWER2##

```{r questionlist, echo = FALSE, results = "asis", results = "hide"}
answerlist(unlist(answers), markup = "markdown")
```

Solution
========
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(unlist(explanations), markup = "markdown")
```

$M_{H_{2}O} = 2 \cdot M_H + M_O = 2 \cdot `r m_h` + `r m_o` = `r m_h2o`$ (g/mol)


Meta-information
================
exname: example_num
extitle: molmass of water 
extype: cloze
exsolution: `r paste(solutions, collapse = "|")`
exclozetype: `r paste(types, collapse = "|")`
extol: `r paste(tolerances, collapse = "|")`
exshuffle: TRUE
exversion: v1