```{r, data generation}
library(knitr)

set.seed(123) # seed for replicability -> removed when generating multiple differnt exercises 

x_mu <- 1000 #set true mean 
alpha = 0.01 #confidence level 
difference <- FALSE # should the means be different? 
n <- 25 #number of observations 


if(difference){
  y_mu <- x_mu + 10 
} else {
  y_mu <- x_mu 
} 

# sample data 
x <- rnorm(n = n, mean = x_mu, sd = 10)
y <- rnorm(n = n, mean = y_mu, sd = 10)


mean_x <- mean(x)
mean_y <- mean(y)
p_value <- t.test(x, y)$p.value


data <- data.frame("Manufacturer_A" = x, "Manufacturer_B" = y)

write.csv2(data, file = "bread_data.csv")

```
Question
======== 
The following data was collected from two bread manufacturers, for each manufacturer, `r n` loaves of bread were weighed. The results is the following data table: 

```{r, data table}
kable(data)

````

The data can be downlaoded as a .csv-file here: 

[](bread_data.csv)


Answer the following questions: 

What is the mean weight of the bread made by manufacturer A? ##ANSWER1##

What is the mean weight of the bread made by manufacturer B? ##ANSWER2## 

Using the function t.test() in R, we can check if the mean weight of the bread differs between the two manufacturerss. Use a signficance level of $\alpha = `r alpha`$

The null hypotheses (H0) is that ##ANSWER3## 

The p-value of the t-test is smaller than $\alpha = `r alpha`$. ##ANSWER4## 

Based on these results, we can ##ANSWER5## 





Solution 
========



Meta-Information
================



