```{r data generation, echo=FALSE, results ='hide'}
include_supplement("ad2stories.R", dir  = "data")
#TODO: import all story elements, sampling process, Q6, other sections 

#sample parameters
n <- sample(20:30, size = 1) # number of data points 
alpha <- sample(c(0.001, 0.01, 0.05, 0.1), size = 1) 

#import stories
source("ad2stories.R", local = TRUE)
story <- sample(stories, size = 1)[[1]] # sample a story 

#rename parameters for better readability 
name <- story$name
text <- story$text
var <- story$var 
unit <- story$unit
mu <- story$mu
sigma <- story$sigma
m <- story$m 
c <- story$c
digit <- story$digit

#data generation (random, no real data)
x <- round(rnorm(n = n, mean = mu, sd = sigma), digits = digit)
y <- round(c + m * x + rnorm(n = n, mean = 0, sd = 5), digits = ifelse(name == "run_heart", digit - 1, digit)) #based on x but with variation 
data <- data.frame(x, y)
names(data) <- var

#plot(x,y)
model <- lm(y ~ x)
p_value <- coef(summary(model))[2, 4]
r2 <- summary(model)$r.squared

```

```{r}
write.csv2(data, file = "ad2_data.csv")
``` 

```{r questions/solutions, echo=FALSE}
answers <- solutions <- explanations <- types <- list()
  
tolerances <- list() 

#ind. var 
answers[[1]] <- var
solutions[[1]] <- c(TRUE, FALSE)
types[[1]] <- "schoice"

#mean var1
answers[[2]] <- ""
solutions[[2]] <- mean(x)
types[[2]] <- "num"
tolerances[[2]] <- 0

#mean var2 
answers[[3]] <- ""
solutions[[3]] <- mean(y)
types[[3]] <- "num"
tolerances[[3]] <- 0

# significant 
answers[[4]] <- c("yes", "no")
solutions[[4]] <- if(p_value < alpha) c(TRUE, FALSE) else c(FALSE, TRUE)
types[[4]] <- "schoice"

# R^2 
answers[[5]] <- ""
solutions[[5]] <- r2
types[[5]] <- "num"
tolerances[[5]] <- 3

# more/less variation 
answers[[6]] <- c("more", "less")
solutions[[6]] <- c(TRUE, FALSE)
types[[6]] <- "schoice"

#perfect R^2
answers[[7]] <- c(1, 0, "$Inf$", -1)
solutions[[7]] <- c(TRUE, FALSE, FALSE, FALSE)
types[[7]] <- "schoice"


```


Questions
=========

`r text` The collected data can be seen in the table below. The `r var[1]` is given in `r unit[1]` and the `r var[2]` is given in `r unit[2]`. 

```{r, table, results="asis"}
knitr::kable(data, format = "markdown")
```


[data.csv](ad2_data.csv)

Answer the following questions. 

Which was the independent variable in the experiment? ##ANSWER1## 

What is the mean `r var[1]`? ##ANSWER2## 

What is the mean `r var[2]`? ##ANSWER3## 

Use the function `lm()` to do a simple linear regression on the data. 

Is the coefficient for the independent variable significant at the significance level $\alpha = `r alpha`$? #ANSWER4# 

What is the $R^2$ of the model? ##ANSWER5## 

The higher the $R^2$, the ##ANSWER6## variation is explained by the model.

The maximum value of the $R^2$ (meaning a perfect correlation in the model) is ##ANSWER7##. 


```{r questions, echo=FALSE}
answerlist(unlist(answers), markup = "markdown")

```

Solutions 
========= 

```{r solutionlist, echo = FALSE, results = "asis"}
# feedback format changed from TRUE/FALSE in a vector to strings "True" and "False"
for (x in 1:length(solutions)) {
  if (types[x] == "schoice") { # only applicable for schoice/mchoice questions
    explanations[x] <- solutions[x] |> lapply(function(x) ifelse(x, "True", "False"))
  } else {
    explanations[x] <- solutions[x]
  }
}

answerlist(unlist(explanations), markup = "markdown") # answerlist for exams2html/exams2moodle created from solutions/explanations list -> feedback
```

```{r meta, echo = FALSE, results = 'hide'}
# change solution format from TRUE/FALSE vector to 1/0 string
for (x in 1:length(solutions)) {
  if (types[x] == "schoice") { # only applicable for schoice/mchoice questions
    solutions[x] <- solutions[x] |>
      unlist() |>
      mchoice2string()
  }
}

for (x in 1:length(solutions)) {
  if (tolerances[x] |> unlist() |> is.null()) {
    tolerances[x] <- 0
  }}
```


Meta-information 
================
exname: Advanced 2
extitle: Advanced 2 `r name`
extype: cloze
exsolution: `r paste(solutions, collapse = "|")`
exclozetype: `r paste(types, collapse = "|")`
extol: `r paste(tolerances, collapse = "|")`
exshuffle: TRUE
exversion: v1





