```{r, data generation}
#TODO: import all story elements, sampling process, Q6, other sections 

n <- sample(20:30, size = 1) # number of data points 
alpha <- sample(c(0.001, 0.01, 0.05, 0.1), size = 1) 


source("ad2_stories.R", local = TRUE)
story <- stories[[1]]

#data generation (random, no real data)
mu <- story$mu
sigma <- story$sigma
var <- story$var
x<- round(rnorm(n = n, mean = mu, sd = sigma), digits = 1)
y <- round(5 + 7 * x + rnorm(n = n, mean = 0, sd = 5), digits = 1) #based on x but with variation 
data <- data.frame(x, y)
names(data) <- var

#plot(x,y)
model <- lm(y ~ x)
p_value <- coef(summary(model))[2, 4]
r2 <- model$r.squared


```

```{r}
write.csv2(data, file = "ad2_data.csv")

``` 

```{r questions/solutions }
answers <- solutions <- explanations <- types <- tolerances <- list() 

#ind. var 
answers[[1]] <- var
solutions[[1]] <- c(TRUE, FALSE)
types[[1]] <- "schoice"

#mean var1
answers[[2]] <- ""
solutions[[2]] <- mean(x)
types[[2]] <- "num"

#mean var2 
answers[[3]] <- ""
solutions[[3]] <- mean(y)
types[[3]] <- "num"

# significant 
answers[[4]] <- c("yes", "no")
solutions[[4]] <- if(p_value < alpha) c(TRUE, FALSE) else c(FALSE, TRUE)
types[[4]] <- "schoice"

# R^2 
answers[[5]] <- ""
solutions[[5]] <- r2
types[[5]] <- "num"

```


Questions
=========

`r text` The collected data can be seen in the table below. The `r var[1]` is given in `r unit[1]` and the `r var[2]` is given in `r unit[2]`. 


[data.csv](ad2_data.csv)

Answer the following questions. 

Which was the independent variable in the experiment? ##ANSWER1## 

What is the mean `r var[1]`? ##ANSWER2## 

What is the mean `r var2[2]`? ##ANSWER3## 

Use the function `lm()` to do a simple linear regression on the data. 

Is the coefficient for the independent variable significant at the significance level $\alpha = `r alpha`$? #ANSWER4# 

What is the $R^2$? ##ANSWER5## 

The higher the R2, the more variation is explained 


