```{r, data generation, echo = FALSE}
library(exams)
answers <- list() 
solutions <- list() 
types <- list()
explanations <- list() 
tolerances <- list()

```

Question
========

IMPORTANT!!! Please remove the knitr-tag "eval = FALSE," from every code block below, these should NOT be used when working with this template, but are necessary for providing such an empty template for download. 


```{r questionlist, eval = FALSE, echo = FALSE, results = "asis"}
# Numerical and text exercises require an empty answerlist entry
for (x in 1:length(types)) {
  if (types[x] %in% c("num", "string")) {
    answers[x] <- ""
  }
}

answerlist(unlist(answers), markup = "markdown")
```

Solution
========

```{r solutionlist, eval = FALSE, echo = FALSE, results = "asis"}
# Change the feedback format from a vector of T/F to (more legiable) strings
for (x in 1:length(solutions)) {
  if (types[x] %in% c("schoice", "mchoice")) {
    explanations[x] <- solutions[x] |> lapply(function(x) ifelse(x, "True", "False"))
  } else {
    explanations[x] <- solutions[x]
  }
}

# Answers are displayed in the feedback 
answerlist(unlist(explanations), markup = "markdown")
```

```{r meta, eval = FALSE, echo = FALSE, results = "hide"}
# Convert the format of single/multiple choice from T/F to 1/0
for (x in 1:length(solutions)) {
  if (types[x] %in% c("schoice", "mchoice")) {
    solutions[x] <- solutions[x] |>
      unlist() |>
      mchoice2string()
  }
}

# Set all undefined tolerances to a default value
for (x in 1:length(solutions)) {
  if (tolerances[x] |> unlist() |> is.null()) {
    tolerances[x] <- 0
  }
}

```

Meta-information 
================
exname:
extitle: 
extype: cloze
exsolution: `r paste(solutions, collapse = "|")`
exclozetype: `r paste(types, collapse = "|")`
extol: `r paste(tolerances, collapse = "|")`
exshuffle: TRUE
exversion: v1